Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-09 article.rnw
Explain the use of non-linear least squares in the methods.

>>>>

The Lotka--Volterra model is not linear in the parameters.
With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters, by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$.
With the rows grouped, however, this becomes impossible, for each species sill has its own growth rate.
As such, the models were fitted by the Gauss--Newton method for non-linear least squares.
